---
title: "linear model with prediction"
author: "Jayline Zelaya"
date: "2023-10-17"
output: html_document
---

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```




## Model1
find an equation that expresses SIMS as a function of ARM.


## Results

### Graphical Results

```{r}
plot(SIMS~ARM,data=data)
```


As arm strength increases sim score increases. This is a positive trend between arm strength and sim score, not a perfect relationship.



### Numerical Results


```{r}
cor(data$SIMS, data$ARM)
```


We have a positive correlation, with noise.


### Inference


```{r}
model1 <- lm(SIMS~ARM,data=data)
summary.lm(model1)
```



```{r}
plot(SIMS~ARM,data=data)
abline(model1, col = 'red')
```


for an increase of 1 in arm strength, sim score increases by 0.0545


```{r}
newdata = data.frame (ARM = 88, GRIP = 94)
predict.lm(model1, newdata,
interval='prediction')
```





## Model2 

Find an equation that expresses SIMS as a function of GRIP.


## Results


## Graphical Results

```{r}
plot(SIMS~GRIP,data=data)
```




As grip strength increases sims score increases.


### Numerical Results

```{r}
cor(data$GRIP, data$SIMS)
```
This is a positive correlation.

### Inference

```{r}
model2 <- lm(SIMS~GRIP,data=data)
summary.lm(model2)
```




```{r}
plot(SIMS~GRIP,data=data)
abline(model2, col = 'red')
```


For an increase in 1 Grip, Sim score increases 0.0454


```{r}
newdata = data.frame (ARM = 88, GRIP = 94)
predict.lm(model2, newdata,
interval='prediction')
```


## Model 3

find an equation that expresses SIMS as a function of ARM+GRIP.

## Results

## Graphical Results

There are no graphical results for model3 because you can't put 2 variables on x or y axis

## Numerical Results


There are no numerical results since we have SIM as a function of 2 variables.


### Inference


```{r}
model3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model3)
```

```{r}
newdata = data.frame (ARM = 88, GRIP = 94)
predict.lm(model3, newdata,
interval='prediction')
```
